\begin{thebibliography}{99}
\bibitem{erdos1945integral}
\textsl{Erd\"{o}s} \textsl{P.} Integral distances /\!/ Bulletin of the
American Mathematical Society. — 1945. — Т. 51, No 12. — С. 996.
\bibitem{anning1945integral}
\textsl{Anning} \textsl{N. H.}, \textsl{Erd\"{o}s} \textsl{P.}
Integral distances /\!/ Bulletin of the American Mathematical
Society. — 1945. — Т. 51, No 8. — С. 598—600.
\bibitem{solymosi2003note}
\textsl{Solymosi} \textsl{J.} Note on integral distances /\!/
Discrete \& Computational Geometry. — 2003. — Т. 30, No 2. —
С. 337—342.
\bibitem{anning1915discussions}
\textsl{Anning} \textsl{N.} Discussions: Relating to a Geometric
Representation of Integral Solutions of Certain Quadratic
Equations /\!/ The American Mathematical Monthly. — 1915. —
Т. 22, No 9. — С. 321—321.
\bibitem{harborth1993upper}
\textsl{Harborth} \textsl{H.},
\textsl{M\"{o}ller} \textsl{M.} An
diameter of integral point sets
Geometry. — 1993. — Т. 9, No 4.
\textsl{Kemnitz} \textsl{A.},
upper bound for the minimum
/\!/ Discrete \& Computational Geometry
— С. 427—432.\bibitem{piepmeyer1996maximum}
\textsl{Piepmeyer} \textsl{L.} The maximum number of odd
integral distances between points in the plane /\!/ Discrete \&
Computational Geometry. — 1996. — Т. 16, No 1. — С. 113—115.
\bibitem{kurz2008bounds}
\textsl{Kurz} \textsl{S.}, \textsl{Laue} \textsl{R.} Bounds for
the minimum diameter of integral point sets /\!/ arXiv preprint
arXiv:0804.1296. — 2008.
\bibitem{our-vvmsh-2018}
\textsl{Авдеев} \textsl{Н. Н.} Некоторые примеры систем
Эрдёша /\!/ Современные методы теории краевых задач :
материалы международной конференции <<Понтрягинские
чтения — XXIX>>, посвященной 90-летию Владимира
Александровича Ильина (2–6 мая 2018 г.) — 2018. — С. 30—31.
\bibitem{locatelli2002packing}
\textsl{Locatelli} \textsl{M.}, \textsl{Raber} \textsl{U.} Packing
equal circles in a square: a deterministic global optimization
approach /\!/ Discrete Applied Mathematics. — 2002. — Т. 122,
No 1—3. — С. 139—166.
\bibitem{costa2013valid}
\textsl{Costa} \textsl{A.} Valid constraints for the point packing
in a square problem /\!/ Discrete Applied Mathematics. — 2013. —
Т. 161, No 18. — С. 2901—2909.
\bibitem{markot2005newverified}
\textsl{Mark